A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-08-15 tidyindex.tex
Update notation sec 3

\begin{itemize}
\item
  \(x\) is the variable in \(\mathbb{R}^p\),
\item
  \(s\) represents the geographic locations in the space
  \(D_s \subseteq \mathbb{R}^m\). This includes a collection of
  countries of interest and paired longitude and latitude coordinates of
  locations, and
\item
  \(t\) denotes the temporal order in \(D_t \subseteq \mathbb{R}^n\).
  Sometimes, it can be time breaks into other temporal components, such
  as year, month, quarter, and season.
\end{itemize}

>>>>

\begin{itemize}
\item
  \(x^j(s, j)\) represents a  variable of interest for example precipitaton, $j = 1, \ldots , p$ and 
\item
  \(s\) represents the geographic location in the space
  \(D_s \subseteq \mathbb{R}^m\). Examples of geographic locations include a collection of
  countries, longitude and latitude coordinates or regions of interest and, 
\item
  \(t\) denotes the temporal measurements in \(D_t \subseteq \mathbb{R}^n\).
  For instance, time measurements could be recorded hourly, yearly, monthly, quaterly or by season.
\end{itemize}
